### 2011-06-12 thesis/background.tex
Semantic Mapping changes.

\begin{description}
\item[One Against All] - in this method $c$ distinct classifiers are trained to
distinguish any class of the remaining ones. The output of all those classifiers
(distance to the separating hyperplane) is then used to categorize the output.
The most common approach is to pick the class with the largest hyperplane
distance. Other variations exists as is the case of using the minimal distance
to the average classification distance of each class~\citep{pronobis2007confidence}.

>>>>

\begin{description}
\item[One Against All] - in this method $c$ distinct classifiers are trained to
distinguish any class of the remaining ones. The output of all those classifiers
(distance to the separating hyperplane) is then used to categorize the output.
The most common approach is to pick the class with the largest hyperplane
distance. Other variations exists as is the case of using the minimal distance
to the average classification distance of each class~\citep{pronobis2007iros}.

### 2011-06-12 thesis/novelty.tex
Semantic Mapping changes.

Additionally it is possible to control variable $b$ states into being only one
of the states of $a$ or $a^*$ by introducing a control variable $c \in {0, 1}$
and factor $\phi_{c}$:
\[
\phi_{c}(b, c) = \left\{
  \begin{array}{l l}
    1, & \qquad \text{if } c = 0 \text{ and } b \in \{A_1,\dotsc,A_n\} \\
    1, & \qquad \text{if } c = 1 \text{ and } b \in \{A^*_1,\dotsc,A^*_n\}\\
    0, & \qquad \text{otherwise}
  \end{array} \right.
\]

@@

\begin{eqnarray*}
 P_B(c=0 | x)         &<& P_B(c=1 | x) \\
\Phi_B(c=0 \land x)   &<& \Phi_B(x=1 \land x) \\
\Phi_G(x) \phi_t(c=0) &<& \Phi_{U_a}(x) \phi_t(c=1) \\
P_G(x) Z_G \phi_t(c=0) &<& P_{U_a}(x) Z_{U_a} \phi_t(c=1) \\
\frac{P_G(x)}{P_{U_a}(x)} &<& \frac{\phi_t(c=1)}{\phi_t(c=0)}\frac{Z_{U_a}}{Z_G}
\end{eqnarray*}

>>>>

Additionally it is possible to control variable $b$ states into being only one
of the states of $a$ or $a^*$ by introducing a control variable $c \in {0, 1}$
and factor $\phi_{c}$:
\[
\phi_{c}(b, c) = \left\{
  \begin{array}{l l}
    1, & \qquad \text{if } c = 0 \text{ and } b \in \{A_1,\dotsc,A_n\} \\
    1, & \qquad \text{if } c = 1 \text{ and } b \in \{A^*_1,\dotsc,A^*_k\}\\
    0, & \qquad \text{otherwise}
  \end{array} \right.
\]

@@

\begin{eqnarray*}
 P_B(c=0 | x)         &<& P_B(c=1 | x) \\
\Phi_B(c=0 \land x)   &<& \Phi_B(x=1 \land x) \\
\Phi_G(x) \phi_t(c=0) &<& \Phi_{U_a}(x) \phi_t(c=1) \\
P_G(x) Z_G \phi_t(c=0) &<& P_{U_a}(x) Z_{U_a} \phi_t(c=1) \\
\frac{P_G(x)}{P_{U_a}(x)} &<& \frac{Z_{U_a}}{Z_G}
\end{eqnarray*}

### 2011-06-12 thesis/semantic-mapping.tex
Semantic Mapping changes.

% Reasoning on why to use semantic mapping
% High-level processing
Also due to uncertainity and complexity 
% Advantages of Multi-modal approaches
%

It is therefore not only for efficiency reasons but also desirable to handle
the information on an high-level probabilistic fashion.

\section{Dora Architecture Overview}
This thesis motivation lies on developing methods for detecting knowledge gaps
on the semantic knowledge of a mobile agent. For that the semantic mapping system
proposed by \cite{pronobis2011phd} was used as a base.

Pronobis presents a system architecture working on indoor environments using
non\hyp{}omnidirectional lasers and visual sensors, that by integrating cues such as geometry,
object presence and appearances is able to perform inference across any semantic property,
for example to handle place categorization.
The introduced semantic representation has not only been tested on real scenarios
and performance measured across several conditions~\cite{pronobis2007iros} but also shown
to be tailored to effectively solve tasks arising on mobile robotics~\cite{hanheide2011ijcai}.
Besides that the system architecture has been drawn with an high-focus on probabilistic
and uncertain reasoning, human interaction and life-long learning capabilities.

>>>>

There has been several efforts in the areas of artificial intelligence and robotics
in creating robots that are able to interact with humans and their environments.
One of the important aspects is to endow those robots with a deeper understanding
of human environments, not just for the purpose of navigation and obstacle avoidance, 
but also in terms of human semantics and functionality.

In that sense the need for semantic mapping arises, and it can be described as the
relation between spatial areas and a set of existent concepts used by humans to
describe them.
Humans associate concepts to areas that relate to the functionality of those. That
association is either useful by explaining where to find certain objects as well to
understand the types of activities to perform on it.
By being able to reason over those semantics an agent can be expected to better
understand human environments and increase its efficiency when performing tasks on them.

It is therefore clear that the need to handle information on an high-level semantic and
probabilistic fashion arises not only for efficiency reasons but also from the desire
of being able to communicate and reason on those aspects.
In order to fully explore the semantic properties and their relations it is necessary to
detect and classify semantic aspects as well to understand the relationships between them.
That conceptual knowledge is important and any limitations on it will limit the capacities
of an agent to reason.

This thesis motivation lies on developing methods for detecting knowledge gaps
on the semantic knowledge of a mobile agent. For that the semantic mapping system
proposed by \cite{pronobis2011phd} was used as a base.

\section{Dora Architecture Overview}
Pronobis presents a system architecture working on indoor environments using
non\hyp{}omnidirectional lasers and visual sensors, that by integrating cues such as geometry,
object presence and appearances is able to perform inference across any semantic property,
for example to handle place categorization.
The introduced semantic representation has not only been tested on real scenarios
and performance measured across several conditions~\cite{pronobis2007iros} but also shown
to be tailored to effectively solve tasks arising on mobile robotics~\cite{hanheide2011ijcai}.
Besides that the system architecture has been drawn with an high-focus on probabilistic
and uncertain reasoning, human interaction and life-long learning capabilities.
